Using Scipion for Stream Image Processing at EM Facilities

### 2018-03-21 3.workflow.tex
casa

 \item \emph{Ume\aa\ Core Facility for Electron Microscopy} (UCEM, \url{http://www.kbc.umu.se/english/ucem})[** Jose Miguel can you verify this?] 
 \item \emph{Science for life Laboratory} (SciLifeLab, \url{http://www.scilifelab.se})
 \item \emph{ESRF Cryo-Electron Microscope} (\url{http://www.esrf.eu/home/UsersAndScience/Experiments/MX/About_our_beamlines/CM01.html})
 \item \emph{Electron Bio-Imaging Centre at Diamond Light Source} (eBIC, \url{http://www.diamond.ac.uk/Science/Integrated-facilities/eBIC.html}) and
 \item \emph{CNB CryoEM Service} (\url{http://www.cnb.csic.es/index.php/en/research/core-facilities/microscopia-crioelectronica})
 \item \emph{Molecular Microscopy Consortium} (\url{https://www.niehs.nih.gov/research/atniehs/facilities/mmc/index.cfm})[**Pablo can you confirm this?]
 \item \emph{National Cancer Institute - NIH} (\url{https://cmm.nci.nih.gov/})[**Pablo can you confirm this?]

@@

SAY WE ARE GOING TO DESCRIBE THREE REPRESENTAIVE CENTER
%\scipion is a very flexible framework that allows to create many different workflows and to choose among several algorithms at each workflow-step. In this work we do not recommend a particular workflow  over others since we realize that different specimens, microscopes or facilities may have different requirements. Nevertheless, since different use cases may clarify \scipionbox capabilities, in the following we describe the pipeline offered by default to the users of three different facilities where \scipion has been installed.

>>>>

 \item \emph{Ume\aa\ Core Facility for Electron Microscopy} (UCEM, \url{http://www.kbc.umu.se/english/ucem})[** Jose Miguel can you verify this?] 
 \item \emph{Science for life Laboratory} (SciLifeLab, \url{http://www.scilifelab.se})
 \item \emph{ESRF Cryo-Electron Microscope} (\url{http://www.esrf.eu/home/UsersAndScience/Experiments/MX/About_our_beamlines/CM01.html})
 \item \emph{Electron Bio-Imaging Centre at Diamond Light Source} (eBIC, \url{http://www.diamond.ac.uk/Science/Integrated-facilities/eBIC.html})
 \item \emph{CNB CryoEM Service} (\url{http://www.cnb.csic.es/index.php/en/research/core-facilities/microscopia-crioelectronica})
 \item \emph{Molecular Microscopy Consortium} (\url{https://www.niehs.nih.gov/research/atniehs/facilities/mmc/index.cfm})[**Pablo can you confirm this?]
 \item \emph{National Cancer Institute - NIH} (\url{https://cmm.nci.nih.gov/})[**Pablo can you confirm this?]

@@

%\scipion is a very flexible framework that allows to create many different workflows and to choose among several algorithms at each workflow-step. In this work we do not recommend a particular workflow  over others since we realize that different specimens, microscopes or facilities may have different requirements. Nevertheless, since different use cases may clarify \scipionbox capabilities, in the following we describe the pipeline offered by default to the users of three different facilities where \scipion has been installed.
